Online Multiclass Linear Classification with Bandit Feedback

### 2019-01-07 arxiv-version/main.tex
minor
ignorant lower bound lemma

% LaTeX packages
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage[singlelinecheck=false]{caption}
\usepackage{fullpage}
\usepackage[colorlinks=true,citecolor=blue,linkcolor=blue]{hyperref}
\usepackage{natbib}
\usepackage{thmtools}
\usepackage{tikz}
\usepackage{color}
\usepackage{comment}

@@

% Math symbols and commands
\newcommand{\calF}{\mathcal{F}}  % set of real numbers
\newcommand{\R}{\mathbb{R}}  % set of real numbers
\newcommand{\indicator}[1]{\mathbf{1}\left[#1 \right]} % indicator
\newcommand{\ip}[2]{\left\langle #1, #2 \right\rangle} % inner product
\newcommand{\norm}[1]{\left\| #1 \right\|}  % norm of a vector or a matrix
%\DeclareMathOperator*{\deg}{deg}
\DeclareMathOperator*{\argmax}{argmax}
\DeclareMathOperator*{\argmin}{argmin}
\DeclareMathOperator*{\Exp}{\mathbf{E}}  % expected value
\DeclareMathOperator{\diff}{d \!} % differential
\DeclareMathOperator*{\polylog}{polylog}

@@

\begin{itemize}
\item \cite{Abernethy-Rakhlin-2009}

\item \cite{Chen-Chen-Zhang-Chen-Zhang-2009}

\item \cite{Hazan-Kale-2011}

\item \cite{Beygelzimer-Orabona-Zhang-2017}

\item \cite{Foster-Kale-Luo-Mohri-Sridharan-2018}

\item \cite{Foster-Krishnamurthy-2018}
\end{itemize}

@@

>>>>

% LaTeX packages
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage[singlelinecheck=false]{caption}
\usepackage{fullpage}
\usepackage[colorlinks=true,citecolor=blue,linkcolor=blue]{hyperref}
\usepackage{natbib}
\usepackage{thmtools}
\usepackage{tikz}
\usepackage{color}
\usepackage{comment}
\usepackage{commath}
\usepackage{dsfont}

@@

% Math symbols and commands
\newcommand{\calF}{\mathcal{F}}
\newcommand{\one}{\mathds{1}}
\newcommand{\R}{\mathbb{R}}  % set of real numbers
\newcommand{\indicator}[1]{\mathbf{1}\left[#1 \right]} % indicator
\newcommand{\ip}[2]{\left\langle #1, #2 \right\rangle} % inner product
%\newcommand{\norm}[1]{\left\| #1 \right\|}  % norm of a vector or a matrix
%\DeclareMathOperator*{\deg}{deg}

\DeclareMathOperator*{\argmax}{argmax}
\DeclareMathOperator*{\argmin}{argmin}
\DeclareMathOperator*{\Exp}{\mathbf{E}}  % expected value
\DeclareMathOperator{\diff}{d \!} % differential
\DeclareMathOperator*{\polylog}{polylog}

@@

%\begin{itemize}
%\item \cite{Abernethy-Rakhlin-2009}

%\item \cite{Chen-Chen-Zhang-Chen-Zhang-2009}

%\item \cite{Hazan-Kale-2011}

%\item \cite{Beygelzimer-Orabona-Zhang-2017}

%\item \cite{Foster-Kale-Luo-Mohri-Sridharan-2018}

%\item \cite{Foster-Krishnamurthy-2018}
%\end{itemize}

%TODO

@@

\begin{lemma}
For any $\gamma \in (0,\frac 1 {160})$,
there exists a set of $N$ examples $x_1, \ldots, x_N$ and vectors $w_1, \ldots, w_N$ ($N = (\Omega(\frac{1}{\gamma}))^{(d-2)/2}$), such that:
$\| x_i \|_2 \leq 1$, $\| w_i \|_2 \leq 1$ for all $i$ in $[N]$, and for all $i, j$ in $[N]$,
\[ w_i \cdot x_j \begin{cases} \geq \gamma ,& i = j, \\ \leq -\gamma ,& i \neq j. \end{cases} \]
\label{lem:embed_d_gamma}
\end{lemma}
\begin{proof}
By Lemma 6 of~\cite{Long1995}, there exists a set of $N = (\frac{1}{2\sqrt{40\gamma}})^{d-2}$ $(d-1)$-dimensional vectors $z_1, \ldots, z_N$ on the unit sphere $\mathbb{S}^{d-2}$, such that
$\theta(z_i, z_j) \geq \sqrt{40 \gamma}$. As $\cos\theta \geq 1-\theta^2/5$ for every $\theta \in [0,\pi]$,
this implies that
\[ z_i \cdot z_j \begin{cases} = 1 ,& i = j, \\ \leq 1- 8\gamma ,& i \neq j. \end{cases} \]

Define $x_i = (\frac12 z_i, \frac12)$, and $w_i = (\frac 12 z_i, -\frac 12(1-4\gamma))$ for all $i$ in $[N]$. It can be easily checked that for all $i$, $\|x_i\| \leq 1$ and $\|w_i\| \leq 1$. In addition,
\[ w_i \cdot x_j = \frac 1 4 z_i \cdot z_j - \frac {1-4\gamma} 4 \begin{cases} \geq \gamma ,& i = j, \\ \leq -\gamma ,& i \neq j. \end{cases}\]
\end{proof}
